COVID-19 dataset strength

### 2020-06-22 covid_dataset_strength/covid_dataset_strength.Rmd
We conclude that for our expected 139.3155572 state transitions, that the dataset is awesome

Based upon nothing but our gut instinct, we base a conclusion on the
number of transitions as shown in the code above.

@@

From that we conclude that for our expected `r n_state_transitions` state
transitions, that our dataset is `r conclusion`.

>>>>

Based on the expected number of transitions, `r n_state_transitions`, we draw a conslusion.

@@

We conclude that for our expected `r n_state_transitions` state
transitions, that the dataset is `r conclusion`.
